---
output:
  word_document: default
  html_document: default
---

This program creates the main results for the cost effectiveness analysis of a nutritional supplementation program for TB patients in India.

First, we calculate the estimated cost per DALY of the intervention and 95% confidence interval. 
```{r}

#bringing in cost effectiveness function and necessary libraries
here::i_am("Code/Cost_Effectiveness_Results.Rmd")
library(here)
source(here("Code/cost_eff.R"))

#setting number of iterations to use for these simulations throughout the program
its<-100

main_run<-cost_eff(iterations = its)
cost_per_daly2<-sort(main_run[["cost_per_daly"]])
quantile(cost_per_daly2,c(0.025,0.5,0.975))

hist(cost_per_daly2[cost_per_daly2<2500&cost_per_daly2>0])

#investigating off center results
plot(main_run[["Treatment_Inputs"]][,"tb_death"][main_run[["cost_per_daly"]]<2500]/
       main_run[["Control_Inputs"]][,"tb_death"][main_run[["cost_per_daly"]]<2500],
     main_run[["cost_per_daly"]][main_run[["cost_per_daly"]]<2500])

#saving for troubleshooting afterward
#saveRDS(main_run,file=here("Data/main_run.RDS"))
```

Now calculating some statistics from the main run to report in the paper.
```{r}
#calculating TB death statistics for first 6 months in control group
tbdeath_con<-vector()
for (i in 1:length(main_run[["Subjects_cont"]])){
  tbdeath_con[i]<-main_run[["Subjects_cont"]][[i]][["die_tb"]][7]
}
#tb death in intervention group (6 months)
tbdeath_trt<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  tbdeath_trt[i]<-main_run[["Subjects_trt"]][[i]][["die_tb"]][7]
}
#risk ratio tb death
tbdeath_rr<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  tbdeath_rr[i]<-main_run[["Subjects_trt"]][[i]][["die_tb"]][7]/
    main_run[["Subjects_cont"]][[i]][["die_tb"]][7]
}
#statistics on tb death
quantile(tbdeath_con,c(0.025,0.5,0.975))
quantile(tbdeath_trt,c(0.025,0.5,0.975))
quantile(tbdeath_rr,c(0.025,0.5,0.975))


#ltf statistics first 6 months treatment group
ltf6_con<-vector()
for (i in 1:length(main_run[["Subjects_cont"]])){
  ltf6_con[i]<-main_run[["Subjects_cont"]][[i]][["ltfu"]][7]
}
#ltf in intervention group (6 months)
ltf6_trt<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  ltf6_trt[i]<-main_run[["Subjects_trt"]][[i]][["ltfu"]][7]
}
#risk ratio ltf 6 months
ltf6_rr<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  ltf6_rr[i]<-main_run[["Subjects_trt"]][[i]][["ltfu"]][7]/
    main_run[["Subjects_cont"]][[i]][["ltfu"]][7]
}
#statistics on ltf
quantile(ltf6_con,c(0.025,0.5,0.975))
quantile(ltf6_trt,c(0.025,0.5,0.975))
quantile(ltf6_rr,c(0.025,0.5,0.975))



#treatment completion rate statistics in control group
comp_con<-vector()
for (i in 1:length(main_run[["Subjects_cont"]])){
  comp_con[i]<-main_run[["Subjects_cont"]][[i]][["early_posttrt"]][7]/10000
}
#treatment completion rate in intervention group
comp_trt<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  comp_trt[i]<-main_run[["Subjects_trt"]][[i]][["early_posttrt"]][7]/10000
}
#risk ratio treatment completion
comp_rr<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  comp_rr[i]<-main_run[["Subjects_trt"]][[i]][["early_posttrt"]][7]/
    main_run[["Subjects_cont"]][[i]][["early_posttrt"]][7]
}
#statistics on treatment completion
quantile(comp_con,c(0.025,0.5,0.975))
quantile(comp_trt,c(0.025,0.5,0.975))
quantile(comp_rr,c(0.025,0.5,0.975))


#lifetime TB deaths control group (tb deaths plus posttb other death*0.14)
tblife_con<-vector()
for (i in 1:length(main_run[["Subjects_cont"]])){
  tblife_con[i]<-main_run[["Subjects_cont"]][[i]][["die_tb"]][720]+
    (0.14*main_run[["Subjects_cont"]][[i]][["die_other_cause_posttb"]][720])
}
#lifetime tb deaths treatment group
tblife_trt<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  tblife_trt[i]<-main_run[["Subjects_trt"]][[i]][["die_tb"]][720]+
    (0.14*main_run[["Subjects_trt"]][[i]][["die_other_cause_posttb"]][720])
}
#risk ratio tb deaths
tblife_rr<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  tblife_rr[i]<-(main_run[["Subjects_trt"]][[i]][["die_tb"]][720]+
    (0.14*main_run[["Subjects_trt"]][[i]][["die_other_cause_posttb"]][720]))/
    (main_run[["Subjects_cont"]][[i]][["die_tb"]][720]+
    (0.14*main_run[["Subjects_cont"]][[i]][["die_other_cause_posttb"]][720]))
}
#statistics on lifetime tb death
quantile(tblife_con,c(0.025,0.5,0.975))
quantile(tblife_trt,c(0.025,0.5,0.975))
quantile(tblife_rr,c(0.025,0.5,0.975))


#DALY aversion
dalyav<-vector()
for (i in 1:length(main_run[["Control_DALYS"]])){
  dalyav[i]<-main_run[["Control_DALYS"]][[i]]-main_run[["Treatment_DALYS"]][[i]]
}
quantile(dalyav,c(0.025,0.5,0.975))


#years lost to TB mortality
#control- more correct method with discounting
yrs_tbdeath_cont_n<-vector()
it_vec<-vector()
it_vec2<-vector()
for (i in 1:length(main_run[["Subjects_cont"]])){
  it_vec<-main_run[["Subjects_cont"]][[i]][["die_tb"]][seq(12,720,12)]
  for (j in 1:length(it_vec)){
      it_vec2[j]<-it_vec[j]/((1+0.03)**j)
  }
  yrs_tbdeath_cont_n[i]<-sum(it_vec2)
}
#intervention- discounting
yrs_tbdeath_trt_n<-vector()
itc_vec<-vector()
itc_vec2<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  itc_vec<-main_run[["Subjects_trt"]][[i]][["die_tb"]][seq(12,720,12)]
  for (j in 1:length(itc_vec)){
      itc_vec2[j]<-itc_vec[j]/((1+0.03)**j)
  }
  yrs_tbdeath_trt_n[i]<-sum(itc_vec2)
}
quantile(yrs_tbdeath_cont_n,c(0.025,0.5,0.975))
quantile(yrs_tbdeath_trt_n,c(0.025,0.5,0.975))

#years lost to incremental post-tb mortality
#control now with discounting
yrs_posttb_cont_n<-vector()
ptb_c<-vector()
ptb_c2<-vector()
for (i in 1:length(main_run[["Subjects_cont"]])){
  ptb_c<-(0.14*sum(main_run[["Subjects_cont"]][[i]][["die_other_cause_posttb"]][seq(12,720,12)]))
  for (j in 1:length(ptb_c)){
       ptb_c2[j]<-ptb_c[j]/((1+0.03)**j)
   }
   yrs_posttb_cont_n[i]<-sum(ptb_c2)
}
#intervention with discounting
yrs_posttb_trt_n<-vector()
ptb_t<-vector()
ptb_t2<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  ptb_t<-(0.14*sum(main_run[["Subjects_trt"]][[i]][["die_other_cause_posttb"]][seq(12,720,12)]))
  for (j in 1:length(ptb_t)){
       ptb_t2[j]<-ptb_t[j]/((1+0.03)**j)
   }
   yrs_posttb_trt_n[i]<-sum(ptb_t2)
}
quantile(yrs_posttb_cont_n,c(0.025,0.5,0.975))
quantile(yrs_posttb_trt_n,c(0.025,0.5,0.975))

#total years lost to TB daly's
#control with discounting
yrs_tbdaly_cont_n<-vector()
dal_c<-vector()
dal_c2<-vector()
for (i in 1:length(main_run[["Subjects_cont"]])){
  dal_c<-unname(0.02775*rowSums(main_run[["Subjects_cont"]][[i]][c("On_TB_tx_M1","On_TB_tx_M2","On_TB_tx_M3","On_TB_tx_M4","On_TB_tx_M5","On_TB_tx_M6","failed","relapse", "repeat_tb_tx_M1","repeat_tb_tx_M2","repeat_tb_tx_M3","repeat_tb_tx_M4","repeat_tb_tx_M5","repeat_tb_tx_M6")]))
  #split months into groups by year
  dcheck1<-split(dal_c,ceiling(seq_along(dal_c)/12))
  
  #summing DALY's by year
    l1<-list()
    for (j in 1:length(dcheck1)){
      l1[j]<-sum(dcheck1[[j]])
    }
    u1<-unlist(l1)
    
  #applying discounting
  for (j in 1:length(u1)){
       dal_c2[j]<-u1[j]/((1+0.03)**j)
   }
  yrs_tbdaly_cont_n[i]<-sum(dal_c2)
}
#intervention- discounting applied
yrs_tbdaly_trt_n<-vector()
dal_t<-vector()
dal_t2<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
 dal_t<-unname(0.02775*rowSums(main_run[["Subjects_trt"]][[i]][c("On_TB_tx_M1","On_TB_tx_M2","On_TB_tx_M3","On_TB_tx_M4","On_TB_tx_M5","On_TB_tx_M6","failed","relapse", "repeat_tb_tx_M1","repeat_tb_tx_M2","repeat_tb_tx_M3","repeat_tb_tx_M4","repeat_tb_tx_M5","repeat_tb_tx_M6")]))
 #split months into groups by year
  dcheck2<-split(dal_t,ceiling(seq_along(dal_t)/12))
  
  #summing DALY's by year
    l2<-list()
    for (j in 1:length(dcheck2)){
      l2[j]<-sum(dcheck2[[j]])
    }
    u2<-unlist(l2)
  
  #applying discounting  
  for (j in 1:length(u2)){
       dal_t2[j]<-u2[j]/((1+0.03)**j)
   }
  yrs_tbdaly_trt_n[i]<-sum(dal_t2)
}
quantile(yrs_tbdaly_cont_n,c(0.025,0.5,0.975))
quantile(yrs_tbdaly_trt_n,c(0.025,0.5,0.975))


#post-TB DALY years lost statistics
#control- discounting applied
yrs_posttbdaly_cont_n<-vector()
pdal_c<-vector()
pdal_c2<-vector()
for (i in 1:length(main_run[["Subjects_cont"]])){
  pdal_c<-unname(0.0044*rowSums(main_run[["Subjects_cont"]][[i]][c("early_posttrt","late_posttrt","ltfu")]))
  #split months into groups by year
  dcheck3<-split(pdal_c,ceiling(seq_along(pdal_c)/12))
  
  #summing DALY's by year
    l3<-list()
    for (j in 1:length(dcheck3)){
      l3[j]<-sum(dcheck3[[j]])
    }
    u3<-unlist(l3)
  for (j in 1:length(u3)){
       pdal_c2[j]<-u3[j]/((1+0.03)**j)
  }
  yrs_posttbdaly_cont_n[i]<-sum(pdal_c2)
}
#intervention- discounting applied
yrs_posttbdaly_trt_n<-vector()
pdal_t<-vector()
pdal_t2<-vector()
for (i in 1:length(main_run[["Subjects_trt"]])){
  pdal_t<-unname(0.0044*rowSums(main_run[["Subjects_trt"]][[i]][c("early_posttrt","late_posttrt","ltfu")]))
  #split months into groups by year
  dcheck4<-split(pdal_t,ceiling(seq_along(pdal_t)/12))
  
  #summing DALY's by year
    l4<-list()
    for (j in 1:length(dcheck4)){
      l4[j]<-sum(dcheck4[[j]])
    }
    u4<-unlist(l4)
    #applying discounting
    for (j in 1:length(u4)){
       pdal_t2[j]<-u4[j]/((1+0.03)**j)
  }
  yrs_posttbdaly_trt_n[i]<-sum(pdal_t2)
}
quantile(yrs_posttbdaly_cont_n,c(0.025,0.5,0.975))
quantile(yrs_posttbdaly_trt_n,c(0.025,0.5,0.975))

#totals
#control
cont_total<-rowSums(cbind(yrs_posttbdaly_cont_n,yrs_tbdaly_cont_n,yrs_posttb_cont_n,yrs_tbdeath_cont_n))
quantile(cont_total,c(0.025,0.5,0.975))
#treatment
trt_total<-rowSums(cbind(yrs_posttb_trt_n,yrs_posttbdaly_trt_n,yrs_tbdaly_trt_n,yrs_tbdeath_trt_n))
quantile(trt_total,c(0.025,0.5,.975))

#total cost statistics
quantile(main_run[["ctrl_csum"]],c(0.025,0.5,0.975))
quantile(main_run[["trt_csum"]],c(0.025,0.5,0.975))

#breaking down costs in intervention group statistics
tbonly_csum<-vector()
rate<-0.03
for (i in 1:length(main_run[["trt_csum"]])){
  Intervention_c<-subset(main_run[["Subjects_trt"]][[i]],select=c("On_TB_tx_M1","On_TB_tx_M2","On_TB_tx_M3","On_TB_tx_M4","On_TB_tx_M5","On_TB_tx_M6",           "repeat_tb_tx_M1","repeat_tb_tx_M2","repeat_tb_tx_M3","repeat_tb_tx_M4","repeat_tb_tx_M5","repeat_tb_tx_M6"))
  
    tbonly_cost<-main_run[["Treatment_Inputs"]][i,"tb_cost"]*Intervention_c 
    sum_dtt<-as.vector(rowSums(tbonly_cost))
    
    #splits months into groups by year
    dcheck1tt<-split(sum_dtt,ceiling(seq_along(sum_dtt)/12))
    
    #summing costs by year
    l1t<-list()
    for (j in 1:length(dcheck1tt)){
      l1t[j]<-sum(dcheck1tt[[j]])
    }
    u1tt<-unlist(l1t)
    
    #applying discounting
    u2tt<-list()
    for (j in 1:length(u1tt)){
      u2tt[j]<-u1tt[j]/((1+rate)**j)
    }
    tbonly_csum[i]<-sum(unlist(u2tt))
}
quantile(tbonly_csum,c(0.025,0.5,0.975))


foodonly_csum<-vector()
rate<-0.03
for (i in 1:length(main_run[["trt_csum"]])){
  Intervention_c<-subset(main_run[["Subjects_trt"]][[i]],select=c("On_TB_tx_M1","On_TB_tx_M2","On_TB_tx_M3","On_TB_tx_M4","On_TB_tx_M5","On_TB_tx_M6",           "repeat_tb_tx_M1","repeat_tb_tx_M2","repeat_tb_tx_M3","repeat_tb_tx_M4","repeat_tb_tx_M5","repeat_tb_tx_M6"))
  
    foodonly_cost<-main_run[["Treatment_Inputs"]][i,"food_cost"]*Intervention_c 
    sum_dtt<-as.vector(rowSums(foodonly_cost))
    
    #splits months into groups by year
    dcheck1tt<-split(sum_dtt,ceiling(seq_along(sum_dtt)/12))
    
    #summing costs by year
    l1t<-list()
    for (j in 1:length(dcheck1tt)){
      l1t[j]<-sum(dcheck1tt[[j]])
    }
    u1tt<-unlist(l1t)
    
    #applying discounting
    u2tt<-list()
    for (j in 1:length(u1tt)){
      u2tt[j]<-u1tt[j]/((1+rate)**j)
    }
    foodonly_csum[i]<-sum(unlist(u2tt))
}
quantile(foodonly_csum,c(0.025,0.5,0.975))


#parameter input statistics
quantile(main_run[["Treatment_Inputs"]][,"tb_death"]/main_run[["Control_Inputs"]][,"tb_death"]
         ,c(0.025,0.5,0.975))

rr<-main_run[["Treatment_Inputs"]][,"tb_death"]/main_run[["Control_Inputs"]][,"tb_death"]
hist(rr)
quantile(main_run[["Treatment_Inputs"]][,"food_cost"],c(0.025,0.5,0.975))
quantile(main_run[["Control_Inputs"]][,"food_cost"],c(0.025,0.5,0.975))


```


Here we run deterministic sensitivity analyses where all parameters except for 1 are held constant to determine the impact of each individual parameter. 

Here are the results from varying only TB death probability.
```{r}
#varying only TB death probability
tbdeath_sens<-cost_eff(iterations=its, tb_death_c=FALSE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=TRUE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE,oth_death_mult_c=TRUE)
summary(tbdeath_sens[["cost_per_daly"]])
quantile(tbdeath_sens[["cost_per_daly"]],c(0.025,0.975))
max(max(tbdeath_sens[["Control_Inputs"]][,"tb_death"]),max(tbdeath_sens[["Treatment_Inputs"]][,"tb_death"]))
min(min(tbdeath_sens[["Control_Inputs"]][,"tb_death"]),min(tbdeath_sens[["Treatment_Inputs"]][,"tb_death"]))

#risk ratio min, median, and max over all the iterations
#tbdeath_sens<-readRDS("tbdeath_sens.RDS")
rr_tbdeath<-c()
for (i in 1:its){
  rr_tbdeath[i]<-tbdeath_sens[["Treatment_Inputs"]][i,"tb_death"]/tbdeath_sens[["Control_Inputs"]][i,"tb_death"]
}
min(rr_tbdeath)
median(rr_tbdeath)
max(rr_tbdeath)
quantile(rr_tbdeath,c(0.025,0.975))

hist(tbdeath_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(tbdeath_sens,file=here("Data/tbdeath_sens.RDS"))

#additional threshold analyses
ts1<-as.data.frame(cbind(tbdeath_sens[["cost_per_daly"]],tbdeath_sens[["Treatment_Inputs"]][,"tb_death"],
           tbdeath_sens[["Control_Inputs"]][,"tb_death"]))
ts1[ts1$V1>549&ts1$V1<552,]
0.012199949/0.01380457
ts1[ts1$V1>409&ts1$V1<410,]
0.00805864/0.01027073
```



Here are the results from varying only other death probability.
```{r}
#varying only Other death probability
othdeath_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=FALSE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=TRUE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE,oth_death_mult_c=TRUE)
summary(othdeath_sens[["cost_per_daly"]])
quantile(othdeath_sens[["cost_per_daly"]],c(0.025,0.975))

#othdeath_sens<-readRDS("othdeath_sens.RDS")
max(max(othdeath_sens[["Control_Inputs"]][,"oth_death"]),max(othdeath_sens[["Treatment_Inputs"]][,"oth_death"]))
median(median(othdeath_sens[["Control_Inputs"]][,"oth_death"]),median(othdeath_sens[["Treatment_Inputs"]][,"oth_death"]))
min(min(othdeath_sens[["Control_Inputs"]][,"oth_death"]),min(othdeath_sens[["Treatment_Inputs"]][,"oth_death"]))

quantile(othdeath_sens[["Control_Inputs"]][,"oth_death"],c(0.025,0.5,0.975))
quantile(othdeath_sens[["Treatment_Inputs"]][,"oth_death"],c(0.025,0.5,0.975))

hist(othdeath_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(othdeath_sens,file=here("Data/othdeath_sens.RDS"))
```


Here are the results from varying only failed probability.
```{r}
#varying only failed probability
fail_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=TRUE, failed_c=FALSE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=TRUE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE,oth_death_mult_c=TRUE)
summary(fail_sens[["cost_per_daly"]])
quantile(fail_sens[["cost_per_daly"]],c(0.025,0.975))
max(max(fail_sens[["Control_Inputs"]][,"failed"]),
    max(fail_sens[["Treatment_Inputs"]][,"failed"]))
min(min(fail_sens[["Control_Inputs"]][,"failed"]),
    min(fail_sens[["Treatment_Inputs"]][,"failed"]))

#risk ratio min and max over all the iterations
#fail_sens<-readRDS("fail_sens.RDS")
rr_fail<-c()
for (i in 1:its){
  rr_fail[i]<-fail_sens[["Treatment_Inputs"]][i,"failed"]/fail_sens[["Control_Inputs"]][i,"failed"]
}
min(rr_fail)
median(rr_fail)
max(rr_fail)
quantile(rr_fail,c(0.025,0.975))

hist(fail_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(fail_sens,file=here("Data/fail_sens.RDS"))

```


Here are the results from varying only LTF probability.
```{r}
#varying only LTF probability
ltf_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=FALSE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=TRUE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE,oth_death_mult_c=TRUE)
summary(ltf_sens[["cost_per_daly"]])
quantile(ltf_sens[["cost_per_daly"]],c(0.025,0.975))

max(max(ltf_sens[["Control_Inputs"]][,"ltf"]),
    max(ltf_sens[["Treatment_Inputs"]][,"ltf"]))
min(min(ltf_sens[["Control_Inputs"]][,"ltf"]),
    min(ltf_sens[["Treatment_Inputs"]][,"ltf"]))

#risk ratio min and max over all the iterations
#ltf_sens<-readRDS("ltf_sens.RDS")
rr_ltf<-c()
for (i in 1:its){
  rr_ltf[i]<-ltf_sens[["Treatment_Inputs"]][i,"ltf"]/ltf_sens[["Control_Inputs"]][i,"ltf"]
}
min(rr_ltf)
median(rr_ltf)
max(rr_ltf)
quantile(rr_ltf,c(0.025,0.5,0.975))

hist(ltf_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(ltf_sens,file=here("Data/ltf_sens.RDS"))
```


Here are the results from varying only LTF to relapse probability.
```{r}
#varying only LTF to relapse
ltfrelap_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=FALSE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=TRUE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE,oth_death_mult_c=TRUE)
summary(ltfrelap_sens[["cost_per_daly"]])
quantile(ltfrelap_sens[["cost_per_daly"]],c(0.025,0.975))

#ltfrelap_sens<-readRDS("ltfrelap_sens.RDS")
max_1<-max(max(ltfrelap_sens[["Control_Inputs"]][,"ltf_relap"]),max(ltfrelap_sens[["Treatment_Inputs"]][,"ltf_relap"]))
median_1<-median(median(ltfrelap_sens[["Control_Inputs"]][,"ltf_relap"]),median(ltfrelap_sens[["Treatment_Inputs"]][,"ltf_relap"]))
min_1<-min(min(ltfrelap_sens[["Control_Inputs"]][,"ltf_relap"]),min(ltfrelap_sens[["Treatment_Inputs"]][,"ltf_relap"]))

lb_1<-quantile(c(ltfrelap_sens[["Control_Inputs"]][,"ltf_relap"],ltfrelap_sens[["Treatment_Inputs"]][,"ltf_relap"]),0.025)
ub_1<-quantile(c(ltfrelap_sens[["Control_Inputs"]][,"ltf_relap"],ltfrelap_sens[["Treatment_Inputs"]][,"ltf_relap"]),0.975)

#converting percentiles to 12 month probabilities
r1<-(-log(1-min_1)) #1 month rate
min_12<-1-exp(-r1*12) #12 month probability
min_12

r1<-(-log(1-median_1)) #1 month rate
median_12<-1-exp(-r1*12) #12 month probability
median_12

r1<-(-log(1-max_1)) #1 month rate
max_12<-1-exp(-r1*12) #12 month probability
max_12

r1<-(-log(1-lb_1)) #1 month rate
lb_12<-1-exp(-r1*12) #12 month probability
lb_12

r1<-(-log(1-ub_1)) #1 month rate
ub_12<-1-exp(-r1*12) #12 month probability
ub_12

hist(ltfrelap_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(ltfrelap_sens,file=here("Data/ltfrelap_sens.RDS"))

```

Here are the results from varying only early post-treatment to relapse probability.
```{r}
#varying only early post treatment to relapse
earptrelap_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=FALSE,ltpt_relap_c=TRUE,
                   food_cost_c=TRUE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE,oth_death_mult_c=TRUE)
summary(earptrelap_sens[["cost_per_daly"]])
quantile(earptrelap_sens[["cost_per_daly"]],c(0.025,0.975))

#earptrelap_sens<-readRDS("earptrelap_sens.RDS")
max_1<-max(max(earptrelap_sens[["Control_Inputs"]][,"earpt_relap"]),max(earptrelap_sens[["Treatment_Inputs"]][,"earpt_relap"]))
median_1<-median(median(earptrelap_sens[["Control_Inputs"]][,"earpt_relap"]),median(earptrelap_sens[["Treatment_Inputs"]][,"earpt_relap"]))
min_1<-min(min(earptrelap_sens[["Control_Inputs"]][,"earpt_relap"]),min(earptrelap_sens[["Treatment_Inputs"]][,"earpt_relap"]))

lb_1<-quantile(c(earptrelap_sens[["Control_Inputs"]][,"earpt_relap"],earptrelap_sens[["Treatment_Inputs"]][,"earpt_relap"]),0.025)
ub_1<-quantile(c(earptrelap_sens[["Control_Inputs"]][,"earpt_relap"],earptrelap_sens[["Treatment_Inputs"]][,"earpt_relap"]),0.975)

#converting min and max to 12 month probabilities
r1<-(-log(1-min_1)) #1 month rate
min_12<-1-exp(-r1*12) #12 month probability
min_12

r1<-(-log(1-median_1)) #1 month rate
median_12<-1-exp(-r1*12) #12 month probability
median_12

r1<-(-log(1-max_1)) #1 month rate
max_12<-1-exp(-r1*12) #12 month probability
max_12

r1<-(-log(1-lb_1)) #1 month rate
lb_12<-1-exp(-r1*12) #12 month probability
lb_12

r1<-(-log(1-ub_1)) #1 month rate
ub_12<-1-exp(-r1*12) #12 month probability
ub_12

hist(earptrelap_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(earptrelap_sens,file=here("Data/earptrelap_sens.RDS"))
```

Here are the results from varying only late post-treatment to relapse probability.
```{r}
#varying only late post treatment to relapse
ltptrelap_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=FALSE,
                   food_cost_c=TRUE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE,oth_death_mult_c=TRUE)
summary(ltptrelap_sens[["cost_per_daly"]])
quantile(ltptrelap_sens[["cost_per_daly"]],c(0.025,0.975))

#ltptrelap_sens<-readRDS("ltptrelap_sens.RDS")
max_1<-max(max(ltptrelap_sens[["Control_Inputs"]][,"ltpt_relap"]),max(ltptrelap_sens[["Treatment_Inputs"]][,"ltpt_relap"]))
median_1<-median(median(ltptrelap_sens[["Control_Inputs"]][,"ltpt_relap"]),median(ltptrelap_sens[["Treatment_Inputs"]][,"ltpt_relap"]))
min_1<-min(min(ltptrelap_sens[["Control_Inputs"]][,"ltpt_relap"]),min(ltptrelap_sens[["Treatment_Inputs"]][,"ltpt_relap"]))

lb_1<-quantile(c(ltptrelap_sens[["Control_Inputs"]][,"ltpt_relap"],ltptrelap_sens[["Treatment_Inputs"]][,"ltpt_relap"]),0.025)
ub_1<-quantile(c(ltptrelap_sens[["Control_Inputs"]][,"ltpt_relap"],ltptrelap_sens[["Treatment_Inputs"]][,"ltpt_relap"]),0.975)

#converting min and max to 12 month probabilities
r1<-(-log(1-min_1)) #1 month rate
min_12<-1-exp(-r1*12) #12 month probability
min_12

r1<-(-log(1-median_1)) #1 month rate
median_12<-1-exp(-r1*12) #12 month probability
median_12

r1<-(-log(1-max_1)) #1 month rate
max_12<-1-exp(-r1*12) #12 month probability
max_12

r1<-(-log(1-lb_1)) #1 month rate
lb_12<-1-exp(-r1*12) #12 month probability
lb_12

r1<-(-log(1-ub_1)) #1 month rate
ub_12<-1-exp(-r1*12) #12 month probability
ub_12

hist(ltptrelap_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(ltptrelap_sens,file=here("Data/ltptrelap_sens.RDS"))
```

Here are the results from varying only food cost.
```{r}

#varying only food cost
foodcost_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=FALSE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE,oth_death_mult_c=TRUE)
quantile(foodcost_sens[["cost_per_daly"]],c(0.025,0.975))

#foodcost_sens<-readRDS("foodcost_sens.RDS")
max(max(foodcost_sens[["Control_Inputs"]][,"food_cost"]),max(foodcost_sens[["Treatment_Inputs"]][,"food_cost"]))
median(median(foodcost_sens[["Control_Inputs"]][,"food_cost"]),median(foodcost_sens[["Treatment_Inputs"]][,"food_cost"]))
min(min(foodcost_sens[["Control_Inputs"]][,"food_cost"]),min(foodcost_sens[["Treatment_Inputs"]][,"food_cost"]))

quantile(c(foodcost_sens[["Control_Inputs"]][,"food_cost"],foodcost_sens[["Treatment_Inputs"]][,"food_cost"]),0.025)
quantile(c(foodcost_sens[["Control_Inputs"]][,"food_cost"],foodcost_sens[["Treatment_Inputs"]][,"food_cost"]),0.975)

hist(foodcost_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(foodcost_sens,file=here("Data/foodcost_sens.RDS"))

#additional threshold analyses
ts2<-as.data.frame(cbind(foodcost_sens[["cost_per_daly"]],foodcost_sens[["Treatment_Inputs"]][,"food_cost"],foodcost_sens[["Control_Inputs"]][,"food_cost"]))
ts2[ts2$V1>549,]
ts2[ts2$V1>409,]
max(foodcost_sens[["Treatment_Inputs"]][,"food_cost"])
max(foodcost_sens[["Control_Inputs"]][,"food_cost"])
```


Here are the results from varying only TB treatment cost.
```{r}
#varying only TB treatment cost
tbcost_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=TRUE,tb_cost_c=FALSE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE,oth_death_mult_c=TRUE)
summary(tbcost_sens[["cost_per_daly"]])
quantile(tbcost_sens[["cost_per_daly"]],c(0.025,0.975))

#tbcost_sens<-readRDS("tbcost_sens.RDS")
max(max(tbcost_sens[["Control_Inputs"]][,"tb_cost"]),max(tbcost_sens[["Treatment_Inputs"]][,"tb_cost"]))
median(median(tbcost_sens[["Control_Inputs"]][,"tb_cost"]),median(tbcost_sens[["Treatment_Inputs"]][,"tb_cost"]))
min(min(tbcost_sens[["Control_Inputs"]][,"tb_cost"]),min(tbcost_sens[["Treatment_Inputs"]][,"tb_cost"]))

quantile(c(tbcost_sens[["Control_Inputs"]][,"tb_cost"],tbcost_sens[["Treatment_Inputs"]][,"tb_cost"]),0.025)
quantile(c(tbcost_sens[["Control_Inputs"]][,"tb_cost"],tbcost_sens[["Treatment_Inputs"]][,"tb_cost"]),0.975)

hist(tbcost_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(tbcost_sens,file=here("Data/tbcost_sens.RDS"))
```


Here are the results from varying only TB DALY value.
```{r}
#varying only TB DALY value
tbdaly_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=TRUE,tb_cost_c=TRUE,tb_daly_c=FALSE,
                   posttb_daly_c=TRUE,oth_death_mult_c=TRUE)
summary(tbdaly_sens[["cost_per_daly"]])
quantile(tbdaly_sens[["cost_per_daly"]],c(0.025,0.975))

#tbdaly_sens<-readRDS("tbdaly_sens.RDS")
max(max(tbdaly_sens[["Control_Inputs"]][,"tb_daly"]),max(tbdaly_sens[["Treatment_Inputs"]][,"tb_daly"]))
median(median(tbdaly_sens[["Control_Inputs"]][,"tb_daly"]),median(tbdaly_sens[["Treatment_Inputs"]][,"tb_daly"]))
min(min(tbdaly_sens[["Control_Inputs"]][,"tb_daly"]),min(tbdaly_sens[["Treatment_Inputs"]][,"tb_daly"]))

quantile(c(tbdaly_sens[["Control_Inputs"]][,"tb_daly"],tbdaly_sens[["Treatment_Inputs"]][,"tb_daly"]),0.025)
quantile(c(tbdaly_sens[["Control_Inputs"]][,"tb_daly"],tbdaly_sens[["Treatment_Inputs"]][,"tb_daly"]),0.975)

hist(tbdaly_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(tbdaly_sens,file=here("Data/tbdaly_sens.RDS"))
```

Here are the results from varying only DALY value after TB.
```{r}
#varying only post TB DALY value
posttbdaly_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=TRUE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=FALSE,oth_death_mult_c=TRUE)
summary(posttbdaly_sens[["cost_per_daly"]])
quantile(posttbdaly_sens[["cost_per_daly"]],c(0.025,0.975))

posttbdaly_sens<-readRDS("posttbdaly_sens.RDS")
max(max(posttbdaly_sens[["Control_Inputs"]][,"posttb_daly"]),max(posttbdaly_sens[["Treatment_Inputs"]][,"posttb_daly"]))
median(median(posttbdaly_sens[["Control_Inputs"]][,"posttb_daly"]),median(posttbdaly_sens[["Treatment_Inputs"]][,"posttb_daly"]))
min(min(posttbdaly_sens[["Control_Inputs"]][,"posttb_daly"]),min(posttbdaly_sens[["Treatment_Inputs"]][,"posttb_daly"]))

quantile(c(posttbdaly_sens[["Control_Inputs"]][,"posttb_daly"],posttbdaly_sens[["Treatment_Inputs"]][,"posttb_daly"]),0.025)
quantile(c(posttbdaly_sens[["Control_Inputs"]][,"posttb_daly"],posttbdaly_sens[["Treatment_Inputs"]][,"posttb_daly"]),0.975)

hist(posttbdaly_sens[["cost_per_daly"]])

#saving for troubleshooting afterward
saveRDS(posttbdaly_sens,file=here("Data/posttbdaly_sens.RDS"))
```


Here are the results from varying only the other death multiplier.
```{r}
#varying only other death multiplier
othdeathmult_sens<-cost_eff(iterations=its, tb_death_c=TRUE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=TRUE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE,oth_death_mult_c=FALSE)
summary(othdeathmult_sens[["cost_per_daly"]])
quantile(othdeathmult_sens[["cost_per_daly"]],c(0.025,0.975))

#saving for troubleshooting afterward
saveRDS(othdeathmult_sens,file=here("Data/othdeathmult_sens.RDS"))

```


Here we create a cost effectiveness graph, showing at what thresholds the intervention is preferable to no intervention. 
```{r}
ce_thresh<-seq(0:2100)
control_ef<-cost_per_daly2
control<-list()
trt<-list()
for (i in 1:length(ce_thresh)){
  control[[i]]<-vector()
  trt[[i]]<-vector()
  for (j in 1:length(control_ef)){
    trt[[i]][j]<-ifelse(ce_thresh[i]>=cost_per_daly2[j],1,0)
    control[[i]][j]<-ifelse(trt[[i]][j]==1,0,1)
  }           
}
prop1<-sapply(control,mean)
prop2<-sapply(trt,mean)
dat<-data.frame(ce_thresh=ce_thresh,prop1=prop1,prop2=prop2)

#getting some more threshold statistics for the paper
dat[dat$ce_thresh==550,]
dat[dat$ce_thresh==410,]
dat[dat$prop2>0.99,]

```

Now plotting this data.
```{r}
# Plot the cost-effectiveness acceptability curve
library(ggplot2)
cgraph<-ggplot( data=dat,aes(x = ce_thresh)) +
  geom_line(aes(y = prop1), color="blue", linetype = "solid") +
  geom_line(aes(y = prop2), color="red", linetype = "solid") +
  labs(x = "Willingness to Pay Threshold", y = "Proportion of Cost-effective Interventions")+
   scale_color_manual(name="Intervention",
                     breaks=c("Nutritional Supplementation", "Control"),
                     values=c("Nutritional Supplementation"="red","Control"="blue"))
cgraph

#saving for publication in figures folder at some point
#save()

```


Below is a two-way sensitivity analysis figure.
```{r message=FALSE, warning=FALSE}
#varying only the two parameters with the most influence in sensitivity analysis
#above
twosens<-cost_eff(iterations=its,tb_death_c=FALSE,
              oth_death_c=TRUE, failed_c=TRUE,ltf_c=TRUE,ltf_relap_c=TRUE,
                   earpt_relap_c=TRUE,ltpt_relap_c=TRUE,
                   food_cost_c=FALSE,tb_cost_c=TRUE,tb_daly_c=TRUE,
                   posttb_daly_c=TRUE)

#saving for troubleshooting afterward
saveRDS(twosens,file=here("Data/twosens.RDS"))

#GAM method for this: removing outliers over 2500 ICER and less than 0 ICER
library(mgcv)
xout<-twosens[["Treatment_Inputs"]][,"food_cost"][twosens[["cost_per_daly"]]<2500&
                                                    twosens[["cost_per_daly"]]>0]
yout<-twosens[["Treatment_Inputs"]][,"tb_death"][twosens[["cost_per_daly"]]<2500&
                                                    twosens[["cost_per_daly"]]>0]/
  twosens[["Control_Inputs"]][,"tb_death"][twosens[["cost_per_daly"]]<2500&
                                                    twosens[["cost_per_daly"]]>0] #this makes it a risk ratio on the y axis
zout<-twosens[["cost_per_daly"]][twosens[["cost_per_daly"]]<2500&
                                                    twosens[["cost_per_daly"]]>0]
mod_lmout <- gam(zout ~ s(xout)+s(yout)) #fitting original GAM
#new data for predicting
newdout<-data.frame(yout=rep(seq(0,1,by=0.0001),each=251),xout=seq(5,75,by=70/250))
#fitting predicted GAM
predout<-as.vector(predict.gam(mod_lmout,newdout))

dataout<-data.frame(cbind(newdout$xout,newdout$yout,predout))
dataout$pred1<-cut(dataout$predout,breaks = c(-Inf,410,550,Inf),right = FALSE)
library(ggplot2)
twoplot<-ggplot(dataout, aes(x=V1,y=V2)) + 
  geom_tile(aes(fill=pred1))+xlab("Food Supplement Monthly Cost ($)")+ylab("Risk Ratio of Death from TB")+guides(fill=guide_legend(title="ICER"))+
 ylim(min=0,max=1)+
  scale_fill_manual(breaks=c("[-Inf,410)", "[410,550)", "[550, Inf)"),
                        values = c("darkgreen", "yellow", "red"),
                        labels=c("<410", "410-549","550+"))
twoplot

#saving two-way plot to avoid weird lines
ggsave(
  here("Figures/twoplot.png"),
  twoplot,
  width = 5,
  height = 5,
  dpi = 1000
)

#extra plots for diagnosing problems
# ggplot(as.data.frame(cbind(xout,yout,zout)),aes(x=xout,y=zout,label=round(yout,digits=2)))+geom_point(aes(color=yout))+geom_text(hjust=0,vjust=0)
# 
# #GAM method for this: not removing outliers at all option
# library(mgcv)
# x<-twosens[["Treatment_Inputs"]][,"food_cost"]
# y<-twosens[["Treatment_Inputs"]][,"tb_death"]/
#   twosens[["Control_Inputs"]][,"tb_death"] #this makes it a risk ratio on the y axis
# z<-twosens[["cost_per_daly"]]
# mod_lm <- gam(z ~ s(x)+s(y)) #fitting original GAM
# #new data for predicting
# newd<-data.frame(y=rep(seq(0,1,by=0.0001),each=251),x=seq(5,50,by=45/250))
# #fitting predicted GAM
# pred<-as.vector(predict.gam(mod_lm,newd))
# 
# data<-data.frame(cbind(newd$x,newd$y,pred))
# data$pred1<-cut(data$pred,breaks = c(-Inf,410,550,Inf),right = FALSE)
# library(ggplot2)
# ggplot(data, aes(x=V1,y=V2)) + 
#   geom_tile(aes(fill=pred1))+xlab("Food Supplement Monthly Cost ($)")+ylab("Monthly Risk Ratio of Death from TB")+guides(fill=guide_legend(title="ICER"))+
#  ylim(min=0,max=1)+
#   scale_fill_manual(breaks=c("[-Inf,410)", "[410,550)", "[550, Inf)"),
#                         values = c("darkgreen", "yellow", "red"),
#                         labels=c("<410", "410-549","550+"))
# 
# #extra plots for diagnosing problems
# ggplot(as.data.frame(cbind(x,y,z)),aes(x=x,y=z,label=round(y,digits=2)))+geom_point(aes(color=y))+geom_text(hjust=0,vjust=0)

#getting threshold values
t1<-dataout[dataout$V1>49 & dataout$predout>549 & dataout$predout<551 & dataout$V2<0.752
            &dataout$V2>0.748,]
t2<-dataout[dataout$V1>30 & dataout$predout>409 & dataout$predout<411& dataout$V2<0.752
            &dataout$V2>0.748,]
t1
t2
#t3<-data[data$V1>79 & data$pred>549 & data$pred<550,]
#t4<-data[data$V1>79 & data$pred>409 & data$pred<410,]
  
```


Below is a survival curve visualizing the death of patients over the study. This
now uses median numbers for each month across the 10,000 iterations.
```{r}
cont<-list()
for (j in 1:its){
  cont[[j]]<-as.vector(main_run[["Subjects_cont"]][[j]][,"die_other_cause_tb"]+
                      main_run[["Subjects_cont"]][[j]][,"die_other_cause_posttb"]+
                         main_run[["Subjects_cont"]][[j]][,"die_tb"])
}
library(dplyr)
cont2<-as.data.frame(do.call(rbind, cont))
survival<-10000-(apply(cont2,2,median))
con<-cbind(survival,"Control",(seq(1:720)/12))

trtt<-list()
for (j in 1:its){
  trtt[[j]]<-as.vector(main_run[["Subjects_trt"]][[j]][,"die_other_cause_tb"]+main_run[["Subjects_trt"]][[j]][,"die_tb"]+main_run[["Subjects_trt"]][[j]][,"die_other_cause_posttb"])
}
library(dplyr)
trtt2<-as.data.frame(do.call(rbind, trtt))
survival<-10000-(apply(trtt2,2,median))
trt<-cbind(survival,"Treatment",(seq(1:720)/12))

# survival<-10000-(main_run[["Subjects_cont"]][,"die_other_cause"]+main_run[["Subjects_cont"]][,"die_tb"])
# con<-cbind(survival,"Control",(seq(1:720)/12))
# survival<-10000-(main_run[["Subjects_trt"]][,"die_other_cause"]+main_run[["Subjects_trt"]][,"die_tb"])
# trt<-cbind(survival,"Treatment",(seq(1:720)/12))


graph<-data.frame(rbind(con,trt))
graph$survival<-as.numeric(graph$survival)
graph$V3<-as.numeric(graph$V3)
library(ggplot2)
survplot<-ggplot(data=graph, aes(x=V3, y=survival, group=factor(V2))) +
  geom_line(aes(color=factor(V2)))+ylab("Surviving Patients")+xlab("Years Since Intervention Start")+theme(legend.title=element_blank())
survplot

#saving figure for publication at some point in figures folder
#save()
```



